A cross-benchmark comparison of Learning to Rank methods

### 2014-05-16 cikm_paper/paper.tex
raamwerk meestertabel :)

\section{Raw Data on Normalised Winning Number for cross-comparison}
\label{app:norm_winnum_all}
\onecolumn
\begin{table*}\centering
\begin{longtable}{@{}rrrrrrrrrrrrrrrrr@{}}\toprule
& \multicolumn{2}{p{0.5cm}}{NDCG@3} & \phantom{a} 
& \multicolumn{2}{c}{NDCG@5} & \phantom{a} 
& \multicolumn{2}{c}{NDG@10} & \phantom{a} 
& \multicolumn{2}{c}{MAP}    & \phantom{a}
& \multicolumn{3}{c}{CROSS}\\
\cmidrule{2-3} \cmidrule{5-6} \cmidrule{8-9} \cmidrule{11-12} \cmidrule{14-16}
Method & NWN & \#ds && NWN & \#ds && NWN & \#ds && NWN & \#ds && WM & IWN & NWN \\ \midrule
AdaRank-MAP & 0.3486 & 12 && 0.3884 & 12 && 0.3648 & 13 && 0.3206 & 12 && 332 & 937 & 0.3543 \\
\bottomrule
\end{longtable}
\caption{Caption}
\end{table*}

>>>>

\section{Raw Data on Normalised Winning Number for cross-comparison}
\label{app:norm_winnum_all}
\onecolumn
\begin{longtable}{@{}rrrrrrrrrrrrrrrrr@{}}\toprule
& \multicolumn{2}{p{0.5cm}}{NDCG@3} & \phantom{a} 
& \multicolumn{2}{c}{NDCG@5} & \phantom{a} 
& \multicolumn{2}{c}{NDG@10} & \phantom{a} 
& \multicolumn{2}{c}{MAP}    & \phantom{a}
& \multicolumn{3}{c}{CROSS}\\
\cmidrule{2-3} \cmidrule{5-6} \cmidrule{8-9} \cmidrule{11-12} \cmidrule{14-16}
Method & NWN & \#ds && NWN & \#ds && NWN & \#ds && NWN & \#ds && WM & IWN & NWN \\ \midrule
AdaRank-MAP & 0.3486 & 12 && 0.3884 & 12 && 0.3648 & 13 && 0.3206 & 12 && 332 & 937 & 0.3543 \\
AdaRank-NDCG & 0.3073 & 12 && 0.3259 & 12 && 0.3158 & 16 && 0.2863 & 12 && 293 & 951 & 0.3081 \\
ADMM & & && & && & && & && & & \\
ApproxAP & & && & && & && & && & & \\
ApproxNDCG & & && & && & && & && & & \\
BagBoo & & && & && & && & && & & \\
Best Single Feature & & && & && & && & && & & \\
BL-MART & & && & && & && & && & & \\
BoltzRank-Pair & & && & && & && & && & & \\
BoltzRank-Single & & && & && & && & && & & \\
BT & & && & && & && & && & & \\
C-CRF & & && & && & && & && & & \\
CA & & && & && & && & && & & \\
CCRank & & && & && & && & && & & \\
CoList & & && & && & && & && & & \\
Consistent-RankCosine & & && & && & && & && & & \\
DCMP & & && & && & && & && & & \\
DirectRank & & && & && & && & && & & \\
EnergyNDCG & & && & && & && & && & & \\
FBPCRank & & && & && & && & && & & \\
FenchelRank & & && & && & && & && & & \\
FocusedBoost & & && & && & && & && & & \\
FocusedNet & & && & && & && & && & & \\
FocusedSVM & & && & && & && & && & & \\
FP-Rank & & && & && & && & && & & \\
FRank & & && & && & && & && & & \\
FSMRank & & && & && & && & && & & \\
FSM$^{SVM}$ & & && & && & && & && & & \\
GAS-E & & && & && & && & && & & \\
GP & & && & && & && & && & & \\
GPRank & & && & && & && & && & & \\
GRankRLS & & && & && & && & && & & \\
GroupCE & & && & && & && & && & & \\
GroupMLE & & && & && & && & && & & \\
IntervalRank & & && & && & && & && & & \\
IPRank & & && & && & && & && & & \\
KeepRank & & && & && & && & && & & \\
Kernel-PCA RankBoost & & && & && & && & && & & \\
KL-CRF & & && & && & && & && & & \\
LAC-MR-OR & & && & && & && & && & & \\
LambdaMART & & && & && & && & && & & \\
LambdaNeuralRank & & && & && & && & && & & \\
LambdaRank & & && & && & && & && & & \\
LARF & & && & && & && & && & & \\
Linear Regression & & && & && & && & && & & \\
ListMLE & & && & && & && & && & & \\
ListNet & & && & && & && & && & & \\
ListReg & & && & && & && & && & & \\
LRUF & & && & && & && & && & & \\
MCP & & && & && & && & && & & \\
MHR & & && & && & && & && & & \\
MultiStageBoost & & && & && & && & && & & \\
NewLoss & & && & && & && & && & & \\
OWPC & & && & && & && & && & & \\
PERF-MAP & & && & && & && & && & & \\
PermuRank & & && & && & && & && & & \\
Q.D.KNN & & && & && & && & && & & \\
RandomForest & & && & && & && & && & & \\
Rank-PMBGP & & && & && & && & && & & \\
RankAggNDCG & & && & && & && & && & & \\
RankBoost & & && & && & && & && & & \\
RankCSA & & && & && & && & && & & \\
RankDE & & && & && & && & && & & \\
RankELM (pairwise) & & && & && & && & && & & \\
RankELM (pointwise) & & && & && & && & && & & \\
RankMGP & & && & && & && & && & & \\
RankNet & & && & && & && & && & & \\
RankRLS & & && & && & && & && & & \\
RankSVM & & && & && & && & && & & \\
RankSVM-Primal & & && & && & && & && & & \\
RankSVM-Struct & & && & && & && & && & & \\
RCP & & && & && & && & && & & \\
RE-QR & & && & && & && & && & & \\
REG-SHG-SDCG & & && & && & && & && & & \\
Ridge Regression & & && & && & && & && & & \\
RSRank & & && & && & && & && & & \\
SmoothGrad & & && & && & && & && & & \\
SmoothRank & & && & && & && & && & & \\
SoftRank & & && & && & && & && & & \\
SparseRank & & && & && & && & && & & \\
SVD-RankBoost & & && & && & && & && & & \\
SVM$^{MAP}$ & & && & && & && & && & & \\
SwarmRank & & && & && & && & && & & \\
TGRank & & && & && & && & && & & \\
TM & & && & && & && & && & & \\
VFLR & & && & && & && & && & & \\
\bottomrule
\caption{Raw data of cross-benchmark comparison}
\label{tab:raw_data}
\end{longtable}
